Neural Neural Textures Make Sim2Real Consistent

### 2022-06-23 CORL/example.tex
Overleaf Merge

%\subsection{Qualitative Evaluation Results}
%We show qualitative evaluation results ....[TODO]
\begin{figure}[th]
	\begin{center}
		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency_diagram.png}
	\end{center}
	\vspace{-7pt}
	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
	\caption{
	    Comparison of image translation methods.
	    The first column is the UVL map as the input.
	    The other columns are results using different image translation methods.
		Each row of images shows a different random placement of objects in the scene.
		TRITON consistently outputs high quality results over different object arrangements. 
		``TRITON texture only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
		% Each column of images is a different image translation algorithm.
		% The same cube is marked with the same color outline across all photos.
		% TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		% Meanwhile, CycleGAN for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		% Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
		% CUT and CycleGAN are not consistent, while TRITON is.
		% TODO: Update the images in this to have the latest training iteration...
		}
		\vspace{-15pt}
		\label{fig:frame_inconsistency_diagram}
	\end{figure}

@@

@@

\clearpage
% The acknowledgments are automatically included only in the final and preprint versions of the paper.
\acknowledgments{}

@@

\clearpage

@@

\section{Appendix} 
\label{sec:appendix}

>>>>

%\subsection{Qualitative Evaluation Results}
%We show qualitative evaluation results ....[TODO]
\begin{figure}[th]
	\begin{center}
		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency_diagram.png}
	\end{center}
	\vspace{-7pt}
	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
	\caption{
	    Comparison of image translation methods.
	    The first column is the UVL map as the input.
	    The other columns are results using different image translation methods.
		Each row of images shows a different random placement of objects in the scene.
		TRITON consistently outputs high quality results over different object arrangements. 
		``TRITON Texture-Only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
		% Each column of images is a different image translation algorithm.
		% The same cube is marked with the same color outline across all photos.
		% TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		% Meanwhile, CycleGAN for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		% Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
		% CUT and CycleGAN are not consistent, while TRITON is.
		% TODO: Update the images in this to have the latest training iteration...
		}
		\vspace{-15pt}
		\label{fig:frame_inconsistency_diagram}
	\end{figure}

@@

\acknowledgments{We thank Srijan Das and Kanchana Ranasinghe for valuable discussions. This work was supported by the National Science Foundation (IIS-2104404 and CNS-2104416).}
%===============================================================================

@@

% \clearpage
% The acknowledgments are automatically included only in the final and preprint versions of the paper.

@@

% \clearpage

@@

\section*{Appendix} 
\label{sec:appendix}
